### 2013-11-15 LaTeX/paper.tex
Updating .gitignore, updating tex file

\documentclass[12pt]{article}
% package includes
% ---------------------

\usepackage{graphicx} % for include images

\usepackage{url}
\usepackage{caption}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\graphicspath{{./Pictures/}}

\title{\textbf{INSERT TITLE HERE}}
\author{Team InsertNumberHere}

\date{November, 2013}

\begin{document}
\maketitle
\newpage
\begin{abstract}
\end{abstract}

\section{Introduction}
\bibliographystyle{chicago}
\bibliography{bibliography}
\end{document}

### 2013-11-15 optimizer.py
stuff

@@ -2,6 +2,8 @@ import numpy as np
 import itertools
 from data import traveltimes, populations
 
+reaches = np.zeros((6, 6))
+
 
 def reach(start, target):
     '''
@@ -9,16 +11,21 @@ def reach(start, target):
     '''
     pass
 
-reaches = np.zeros((6, 6))
-for i in xrange(6):
-    for j in xrange(6):
-        reaches[i, j] = reach(i, j)
 
-maxreach = 0
-optimal = (0, 1, 2)
-for a1, a2, a3 in itertools.combinations(xrange(6), 3):
-    totalreach = 0
+def calcreaches():
+    global reaches
     for i in xrange(6):
-        totalreach += min(populations[i], sum([reaches[a, i] for a in (a1, a2, a3)]))
-    if totalreach > maxreach:
-        optimal = (a1, a2, a3)
+        for j in xrange(6):
+            reaches[i, j] = reach(i, j)
+
+
+def bruteforce():
+    maxreach = 0
+    optimal = (0, 1, 2)
+    for a1, a2, a3 in itertools.combinations(xrange(6), 3):
+        totalreach = 0
+        for i in xrange(6):
+            totalreach += min(populations[i], sum([reaches[a, i] for a in (a1, a2, a3)]))
+        if totalreach > maxreach:
+            optimal = (a1, a2, a3)
+    return optimal

### 2013-11-15 optimizer.py
Added greedy shit

@@ -2,7 +2,8 @@ import numpy as np
 import itertools
 from data import traveltimes, populations
 
-reaches = np.zeros((6, 6))
+NODES = 6
+reaches = np.zeros((NODES, NODES))
 
 
 def reach(start, target):
@@ -13,19 +14,36 @@ def reach(start, target):
 
 
 def calcreaches():
-    global reaches
-    for i in xrange(6):
-        for j in xrange(6):
+    for i in xrange(NODES):
+        for j in xrange(NODES):
             reaches[i, j] = reach(i, j)
 
 
-def bruteforce():
+def greedyoptimize(nambulances):
+    reached = np.zeros(NODES)
+    startnodes = np.empty(nambulances)
+    for i in xrange(nambulances):
+        maxreach = 0
+        bestnode = 0
+        for start in xrange(NODES):
+            reach = 0
+            for target in xrange(NODES):
+                reach += min(reaches[start, target], populations[target] - reached[target])
+            if reach > maxreach:
+                maxreach = reach
+                bestnode = start
+        startnodes[i] = bestnode
+        for target in xrange(NODES):
+            reached[target] += min(reaches[start, target], populations[target] - reached[target])
+    return (startnodes, reached)
+
+
+def bruteforce(nambulances):
     maxreach = 0
-    optimal = (0, 1, 2)
-    for a1, a2, a3 in itertools.combinations(xrange(6), 3):
+    for startingnodes in itertools.combinations(xrange(NODES), nambulances):
         totalreach = 0
-        for i in xrange(6):
-            totalreach += min(populations[i], sum([reaches[a, i] for a in (a1, a2, a3)]))
+        for i in xrange(NODES):
+            totalreach += min(populations[i], sum([reaches[a, i] for a in startingnodes]))
         if totalreach > maxreach:
-            optimal = (a1, a2, a3)
+            optimal = startingnodes
     return optimal

### 2013-11-16 Code/optimizer.py
whooo

@@ -1,16 +1,63 @@
 import numpy as np
+import sympy as sp
+from sympy import Function, integrate
 import itertools
 from data import traveltimes, populations
 
 NODES = 6
 reaches = np.zeros((NODES, NODES))
 
+a, x, s, t = sp.symbols('a, x, s, t')
+
+
+class quad_curve(Function):
+    nargs = 2
+
+    @classmethod
+    def eval(cls, a, x):
+        return -(12.0 / 11 / a) * x ** 2 / a ** 2 + (12.0 / 11 / a)
+
+
+class const_curve(Function):
+    nargs = 2
+
+    @classmethod
+    def eval(cls, a, x):
+        return 1 / a
+
+
+class gauss_curve(Function):
+    nargs = 2
+
+    @classmethod
+    def eval(cls, a, x):
+        return 0  # TODO
+
+PROB_CURVE = quad_curve
+MAX_TIME = 8
+
+expected_value = integrate(integrate(PROB_CURVE(a, t) * PROB_CURVE(a, t - s),
+                                     (t, -a / 2, a / 2)) * s,
+                           (s, 0, a))
+
 
 def reach(start, target):
     '''
     Calculates reach of a single ambulance for a district
     '''
-    pass
+    #taa = traveltimes[start, start]
+    tbb = traveltimes[target, target]
+    tab = traveltimes[start, target]
+    tba = traveltimes[target, start]
+    #taam = 2 * taa / (1 + tba / tab)
+    tbbp = 2 * tbb / (1 + tab / tba)
+    #wa = sp.solve(expected_value - taam)[0]
+    wb = sp.solve(expected_value - tbbp)[0]
+    bstart = -wb / 2
+    bend = MAX_TIME - tab
+    if bstart > bend:
+        return 0
+    return round(integrate(PROB_CURVE(wb, t), (t, bstart, bend)) * populations(target))
 
 
 def calcreaches():

### 2013-11-16 Code/data.py
whoooo yeah it sort of works

@@ -16,4 +16,4 @@ traveltimes = np.array([[1, 8, 12, 14, 10, 16],
 Populations of each sector.
 0-indexed, watch out!
 '''
-populations = np.array((5e4, 8e4, 3e4, 5.5e4, 3.5, 2e4))
+populations = np.array((5e4, 8e4, 3e4, 5.5e4, 3.5e4, 2e4))

### 2013-11-16 Code/optimizer.py

@@ -46,18 +46,18 @@ def reach(start, target):
     Calculates reach of a single ambulance for a district
     '''
     #taa = traveltimes[start, start]
-    tbb = traveltimes[target, target]
-    tab = traveltimes[start, target]
-    tba = traveltimes[target, start]
-    #taam = 2 * taa / (1 + tba / tab)
-    tbbp = 2 * tbb / (1 + tab / tba)
-    #wa = sp.solve(expected_value - taam)[0]
-    wb = sp.solve(expected_value - tbbp)[0]
-    bstart = -wb / 2
-    bend = MAX_TIME - tab
+tbb = traveltimes[target, target]
+tab = traveltimes[start, target]
+tba = traveltimes[target, start]
+#taam = 2 * taa / (1 + tba / tab)
+tbbp = 2 * tbb / (1 + tab / tba)
+#wa = sp.solve(expected_value - taam)[0]
+wb = sp.solve(expected_value - tbbp)[0]
+bstart = -wb / 2
+bend = min(wb / 2, MAX_TIME - tab)
     if bstart > bend:
         return 0
-    return round(integrate(PROB_CURVE(wb, t), (t, bstart, bend)) * populations(target))
+    return round(integrate(PROB_CURVE(wb, t), (t, bstart, bend)) * populations[target])
 
 
 def calcreaches():

### 2013-11-16 Code/optimizer.py
whoops ooh yeah

@@ -46,15 +46,15 @@ def reach(start, target):
     Calculates reach of a single ambulance for a district
     '''
     #taa = traveltimes[start, start]
-tbb = traveltimes[target, target]
-tab = traveltimes[start, target]
-tba = traveltimes[target, start]
-#taam = 2 * taa / (1 + tba / tab)
-tbbp = 2 * tbb / (1 + tab / tba)
-#wa = sp.solve(expected_value - taam)[0]
-wb = sp.solve(expected_value - tbbp)[0]
-bstart = -wb / 2
-bend = min(wb / 2, MAX_TIME - tab)
+    tbb = traveltimes[target, target]
+    tab = traveltimes[start, target]
+    tba = traveltimes[target, start]
+    #taam = 2 * taa / (1 + tba / tab)
+    tbbp = 2 * tbb / (1 + tab / tba)
+    #wa = sp.solve(expected_value - taam)[0]
+    wb = sp.solve(expected_value - tbbp)[0]
+    bstart = -wb / 2
+    bend = min(wb / 2, MAX_TIME - tab)
     if bstart > bend:
         return 0
     return round(integrate(PROB_CURVE(wb, t), (t, bstart, bend)) * populations[target])

### 2013-11-16 Code/optimizer.py
we need sleep

@@ -60,10 +60,9 @@ def reach(start, target):
     return round(integrate(PROB_CURVE(wb, t), (t, bstart, bend)) * populations[target])
 
 
-def calcreaches():
-    for i in xrange(NODES):
-        for j in xrange(NODES):
-            reaches[i, j] = reach(i, j)
+for i in xrange(NODES):
+    for j in xrange(NODES):
+        reaches[i, j] = reach(i, j)
 
 
 def greedyoptimize(nambulances):
@@ -73,6 +72,8 @@ def greedyoptimize(nambulances):
         maxreach = 0
         bestnode = 0
         for start in xrange(NODES):
+            if start in startnodes:
+                continue  # don't duplicate
             reach = 0
             for target in xrange(NODES):
                 reach += min(reaches[start, target], populations[target] - reached[target])
@@ -81,16 +82,18 @@ def greedyoptimize(nambulances):
                 bestnode = start
         startnodes[i] = bestnode
         for target in xrange(NODES):
-            reached[target] += min(reaches[start, target], populations[target] - reached[target])
+            reached[target] += min(reaches[bestnode, target], populations[target] - reached[target])
     return (startnodes, reached)
 
 
 def bruteforce(nambulances):
-    maxreach = 0
+    maxreach = np.zeros(1)
     for startingnodes in itertools.combinations(xrange(NODES), nambulances):
-        totalreach = 0
-        for i in xrange(NODES):
-            totalreach += min(populations[i], sum([reaches[a, i] for a in startingnodes]))
-        if totalreach > maxreach:
+        reached = np.zeros(NODES)
+        for target in xrange(NODES):
+            for start in startingnodes:
+                reached[target] += min(reaches[start, target], populations[target] - reached[target])
+        if np.sum(reached) > np.sum(maxreach):
             optimal = startingnodes
-    return optimal
+            maxreach = reached
+    return (optimal, maxreach)

### 2013-11-16 Code/optimizer.py
Added comments

@@ -4,11 +4,14 @@ from sympy import Function, integrate
 import itertools
 from data import traveltimes, populations
 
-NODES = 6
+NODES = 6  # number of nodes to care about
+MAX_TIME = 8  # maximum allotted time to reach a destination
 reaches = np.zeros((NODES, NODES))
 
 a, x, s, t = sp.symbols('a, x, s, t')
 
+
+# Probability/population distribution curves. Who knows what these do.
 
 class quad_curve(Function):
     nargs = 2
@@ -33,17 +36,14 @@ class gauss_curve(Function):
     def eval(cls, a, x):
         return 0  # TODO
 
-PROB_CURVE = quad_curve
-MAX_TIME = 8
+PROB_CURVE = quad_curve  # selected model for population distribution
 
-expected_value = integrate(integrate(PROB_CURVE(a, t) * PROB_CURVE(a, t - s),
-                                     (t, -a / 2, a / 2)) * s,
-                           (s, 0, a))
+expected_value = integrate(integrate(PROB_CURVE(a, t) * PROB_CURVE(a, t - s), (t, -a / 2, a / 2)) * s, (s, 0, a))
 
 
 def reach(start, target):
     '''
-    Calculates reach of a single ambulance for a district
+    Calculates reach of a single ambulance for a district.
     '''
     #taa = traveltimes[start, start]
     tbb = traveltimes[target, target]
@@ -66,6 +66,11 @@ for i in xrange(NODES):
 
 
 def greedyoptimize(nambulances):
+    '''
+    Optimize ambulance placement using a greedy algorithm.
+    Selects additional ambulances based on how
+    many additional people it would cover.
+    '''
     reached = np.zeros(NODES)
     startnodes = np.empty(nambulances)
     for i in xrange(nambulances):
@@ -73,7 +78,7 @@ def greedyoptimize(nambulances):
         bestnode = 0
         for start in xrange(NODES):
             if start in startnodes:
-                continue  # don't duplicate
+                continue  # don't duplicate zones
             reach = 0
             for target in xrange(NODES):
                 reach += min(reaches[start, target], populations[target] - reached[target])
@@ -87,7 +92,11 @@ def greedyoptimize(nambulances):
 
 
 def bruteforce(nambulances):
-    maxreach = np.zeros(1)
+    '''
+    Takes all possible combinations of nambulances from NODES,
+    and arranges them so that there is maximum coverage among zones.
+    '''
+    maxreach = np.zeros(NODES)
[…]

### 2013-11-16 LaTeX/paper.tex
Adding team number
Updating paper layout, outlining next 23 hours
Reformatting tex, upgrading plan for the next 22 hours
Adding problem restatement

@@
-\documentclass[12pt]{article}
+\documentclass[notitlepage, 12pt]{article}
 % package includes
@@
 \usepackage{fullpage}
+\usepackage{fancyhdr}
 \usepackage{amsmath}
@@
 
+% \pagestyle{fancy}
+% \lhead{Team 4552}
+% \chead{Problem A}
+% \rhead{}
+
+% \renewcommand{\headrulewidth}{0.8pt}
+% \renewcommand{\footrulewidth}{0.8pt}
+
 \title{\textbf{INSERT TITLE HERE}}
-\author{Team InsertNumberHere}
+\author{Team 4552}
 
-\date{November, 2013}
+\date{November 15, 2013}
 
@@
 \maketitle
+
+\tableofcontents
 \newpage
-\begin{abstract}
-\end{abstract}
+\section{Problem Restatement}
+Given a fictitious district made up of six separate zones, and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
+Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.
 
-\section{Introduction}
+Then, consider a scenario in which a large scale disaster affects a single location (i.e.
+9/11), and discuss how an Emergency Service Coordinator would cover the situation.
+Examine how a real-world city or county would prepare for such a disaster.
+Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.
+
+\section{Assumptions and Justifications}
+
+\section{The Model}
+
+\subsection{Model Approach}
+
+\subsection{Part 1?}
+
+\subsection{Part 2?}
+
+\section{Model Analysis}
+
+\subsection{3 Ambulance Cover}
+
+\subsection{2 Ambulance Cover}
+
+\subsection{1 Ambulance Cover}
+
+\subsection{Catastrophic Cover}
+
+\section{Strengths and Weaknesses}
+
+\section{Extensions}
+
+\section{Non-Technical Memo}
+
+\appendix
+\section{Code}
+
 \bibliographystyle{chicago}

### 2013-11-16 LaTeX/paper.tex
added stuff about catastrophic cover

@@
 \subsection{Catastrophic Cover}
+In a localized catastrophic event such as those that happened on September 11, 2001, there will be
+many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
+such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
+injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
+reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
+location of the emergency.
+
+Catastrophic events will cause more casualties than emergency personnel will be able to service, so as a result,
+ambulances will have to act as shuttles to hospitals for the injured. Therefore, to maximize throughput
+cities should arrange hospitals to minimize the average time between all areas and the nearest
+hospital.
+
+Since metropolitan areas are most likely to be affected by catastrophic events, and catastrophic events there
+will affect significantly more people, to maximize patient throughput cities should arrange hospitals to minimize
+the average time between all areas and the nearest hospital. Futhermore, due to differences in population density,
+statistically, an accident in a metropolitan area will demand more urgent care than a similar accident
+in a rural or suburban area. Therefore, when the city lays out its stations for ambulances, attempting to minimize
+travel times to any area, it should put significantly more weight on minimizing travel time to metropolitan areas.
 

### 2013-11-16 LaTeX/paper.tex
Ray fucked up

@@
 \section{Assumptions and Justifications}
+\begin{enumerate}
+    \item The travel times given are calculated from an optimal route from the center of the first
+        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
+        via an indirect route from the direct, given one.
+    \item The travel times given for travel from any zone to itself is the average
+        of all the travel times of the different routes within that zone.
+    \item The ratio between the time it takes inside a zone to travel toward a second zone,
+        to the time it takes inside a zone to return from a second, is equal to the ratio
+        between the travel time from the first zone to the second, and the travel time from the
+        second to the first.
+    \item
+        Ambulances can only be placed in the very center of a zone. Because we do not know the
+        spacial position of the zones relative to each other, we cannot consider the ambulances
+        being closer to one zone or another.
+    \item
+        Overlap of ambulance coverage in a zone will be treated as even coverage over the entire
+        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, due to
+        ambulances  %TODO
 

### 2013-11-16 LaTeX/paper.tex
fixed assumption five

@@
     \item
-        Overlap of ambulance coverage in a zone will be treated as even coverage over the entire
-        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, due to
-        ambulances  %TODO
+       Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
+        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume that multiple ambulances will cover different areas of the zones, thus evening out coverage.
 

### 2013-11-16 LaTeX/paper.tex
added a def

--- 2013-11-16 LaTeX/paper.tex
@@
 \subsection{Part 1?}
+An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
+that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
+zone-to-zone coverage.
 
-\subsection{Part 2?}
+\subsection{Ambulance Distributor}
+Once the zone-to-zone coverages have been
 

### 2013-11-16 LaTeX/paper.tex

--- 2013-11-16 LaTeX/paper.tex
@@
         Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
-        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume that multiple ambulances will cover different areas of the zones, thus evening out coverage.
+        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
+        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
 

### 2013-11-16 LaTeX/paper.tex
fixed bug
Added definitions for part 1

@@
         that multiple ambulances will cover different areas of the zones, thus evening out coverage.
+\end{enumerate}
 
@@
 zone-to-zone coverage.
+\begin{description}
+    \item[A(t) and B(t)] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution.
+    \item[v] required ambulance response time
+    \item[T_{AB}] travel time from A to B, given
+    \item[T_{BA}] travel time from B to A, given
+    \item[P_B] total population of B
+    \item[T_{A-}] travel time inside of A traveling toward B
+    \item[T_{B+}] travel time inside of B traveling away from A
+    \item[a and b] width of A and B respectively
+    \item[g] width of the gap between A and B
+\end{description}
 

### 2013-11-16 LaTeX/paper.tex
Added function for Z_AB(t) and added variables

--- 2013-11-16 LaTeX/paper.tex
@@
 zone-to-zone coverage.
+\begin{description}
+    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
+    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
+    \item[$v$] required ambulance response time
+    \item[$T_{AB}$] travel time from A to B, given
+    \item[$T_{BA}$] travel time from B to A, given
+    \item[$P_B$] total population of B
+    \item[$T_{A^+}$] travel time inside of A traveling away from B
+    \item[$T_{A^-}$] travel time inside of A traveling toward B
+    \item[$T_{B^+}$] travel time inside of B traveling away from A
+    \item[$T_{B^-}$] travel time inside of B traveling toward A
+    \item[$a, b$] width of A and B respectively
+    \item[$g$] width of the gap between A and B
+\end{description}
+
+%TODO: Graphical representation of origin and setup
+The function for zone-to-zone coverage in respect to travel time can be written out as 
+$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
 

### 2013-11-16 LaTeX/paper.tex
Adding to extensions section

--- 2013-11-16 LaTeX/paper.tex
@@
 \section{Assumptions and Justifications}
-\begin{enumerate}
-    \item The travel times given are calculated from an optimal route from the center of the first
-        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
-        via an indirect route from the direct, given one.
-    \item The travel times given for travel from any zone to itself is the average
-        of all the travel times of the different routes within that zone.
-    \item The ratio between the time it takes inside a zone to travel toward a second zone,
-        to the time it takes inside a zone to return from a second, is equal to the ratio
-        between the travel time from the first zone to the second, and the travel time from the
-        second to the first.
-    \item
-        Ambulances can only be placed in the very center of a zone. Because we do not know the
-        spacial position of the zones relative to each other, we cannot consider the ambulances
-        being closer to one zone or another.
-    \item
-        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
-        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
-        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
 
@@
 \subsection{Part 1?}
-An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
-zone-to-zone coverage.
 
-\subsection{Ambulance Distributor}
-Once the zone-to-zone coverages have been
+\subsection{Part 2?}
 
@@
 \subsection{Catastrophic Cover}
-In a localized catastrophic event such as those that happened on September 11, 2001, there will be
-many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
-such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
-injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
-reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
-location of the emergency.
-
-Catastrophic events will cause more casualties than emergency personnel will be able to service, so as a result,
-ambulances will have to act as shuttles to hospitals for the injured. Therefore, to maximize throughput
-cities should arrange hospitals to minimize the average time between all areas and the nearest
-hospital.
-
-Since metropolitan areas are most likely to be affected by catastrophic events, and catastrophic events there
-will affect significantly more people, to maximize patient throughput cities should arrange hospitals to minimize
-the average time between all areas and the nearest hospital. Futhermore, due to differences in population density,
-statistically, an accident in a metropolitan area will demand more urgent care than a similar accident
-in a rural or suburban area. Therefore, when the city lays out its stations for ambulances, attempting to minimize
-travel times to any area, it should put significantly more weight on minimizing travel time to metropolitan areas.
 
@@
 \section{Extensions}
+Though our model performs fairly well already, providing us with the optimal locations of our $n$ ambulances to maximize the number of people saved, there are a number of ways we can improve the model so that we can make more accurate predictions as to the number of people we can reach in an eight minute period.
+Furthermore, we can also improve the overall efficiency of the solution algorithm itself, by looking at potential dynamic programming approaches to the problem.
+
+While any algorithmic changes may not be necessary with only six zones, and a maximum of $n = 3$ ambulances, if we scale this problem up to a large city, or across multiple counties, algorithm efficiency becomes an important problem that requires attention.
+
+\subsection{Population Distribution}
+As it currently stands, we have very little information regarding the actual population distribution of each zone in the scope of the district, which provides us with a slightly skewed perception.
+While we justified the use of a standard distribution for population above, we have the ability to greatly improve our model with a better idea of how spread out a population of a zone actually is, in relation to its epicenter.
+This information allows us to better predict how many people an ambulance would miss (not be able to cover) in a certain zone.
+
+The number of missed people is an important statistic that an Emergency Service Coordinator needs to have in order to fully optimize their resources.
+In our system now, we predict this number with a certain level of accuracy, but we are still prone to a relatively large amount of error.
+With a better understanding of the population and geospacial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.
+
+\subsection{Dynamic Approach}
+With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is not a pressing issue.
+As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligent amount of time.
+However, as we look to expanding the model to fit a larger area, with more zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.
+
+Even after our greedy algorithm reduces the overall solution time to an $O(n^2)$, or polynomial time, there are still possible ways to improve it.
+One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together.
+As a result of such a method, we would reduce the problem to one with an $O(nlog(n))$, an algorithm that would easily scale to larger data sets.
+
+However, the implementation of such a method is slightly less simple. One such way to implement a solution in this manner would be in the following fashion:
+
+\begin{enumerate}
+\item Given a graph of each node (zone), and the edges between them (time it takes to travel between nodes), immediately remove all infeasible edges, with edge length (time) greater than the eight minute baseline.
+
+\item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential split points, to divide each district into smaller subdistricts.
+Make sure to account for overlap.
+
+\item Allocate $n$ ambulances across each subdistrict.
+If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance)
+
+\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole
+\end{enumerate}
+
+While we are not guaranteed to find the optimal solution to ambulance location, we will be provided with a relatively good one, in a short amount of time.
+There are tradeoffs to using such a model, but especially at a large scale, this methodology is realistically the one an Emergency Service Coordinator would use.
 

### 2013-11-16 LaTeX/paper.tex
Adding title WIP

--- 2013-11-16 LaTeX/paper.tex
@@
 
-\title{\textbf{INSERT TITLE HERE}}
+\title{\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}}
 \author{Team 4552}

### 2013-11-16 LaTeX/paper.tex
wrote in Ambulance Distribution Optimization

--- 2013-11-16 LaTeX/paper.tex
@@
 \begin{enumerate}
-    \item The travel times given are calculated from an optimal route from the center of the first
+    \item
+        The travel times given are calculated from an optimal route from the center of the first
         zone to the center of ths econd. This excludes the possibility of reaching a zone faster
         via an indirect route from the direct, given one.
-    \item The travel times given for travel from any zone to itself is the average
+    \item
+        The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item The ratio between the time it takes inside a zone to travel toward a second zone,
+    \item
+        The ratio between the time it takes inside a zone to travel toward a second zone,
         to the time it takes inside a zone to return from a second, is equal to the ratio
@@
     \item
-        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
+        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
         that multiple ambulances will cover different areas of the zones, thus evening out coverage.
+        (If partial coverages from multiple ambulances sum to above the total population of a zone,
+        we assume that zone is completely covered by the ambulances.)
 \end{enumerate}
@@
 zone-to-zone coverage.
-\begin{description}
-    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
-    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
-    \item[$v$] required ambulance response time
-    \item[$T_{AB}$] travel time from A to B, given
-    \item[$T_{BA}$] travel time from B to A, given
-    \item[$P_B$] total population of B
-    \item[$T_{A^+}$] travel time inside of A traveling away from B
-    \item[$T_{A^-}$] travel time inside of A traveling toward B
-    \item[$T_{B^+}$] travel time inside of B traveling away from A
-    \item[$T_{B^-}$] travel time inside of B traveling toward A
-    \item[$a, b$] width of A and B respectively
-    \item[$g$] width of the gap between A and B
-\end{description}
 
-%TODO: Graphical representation of origin and setup
-The function for zone-to-zone coverage in respect to travel time can be written out as 
-$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
+\subsection{Ambulance Distributon Optimization}
+Once the zone-to-zone coverages have been calculated, we must still decide where to place
+the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
+of the individual zones, i.e. the number of people that can be reached by at least one ambulance
+within eight minutes.
 
-\subsection{Ambulance Distributor}
-Once the zone-to-zone coverages have been
+Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
+zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
+coverage.
+
+Under the given conditions, we can easily find the optimal ambulance placement using a brute force
+method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
+However, this solution is not scalable to larger cities, as the brute force method has time complexity
+$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
+becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
+and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
+coverages for each of the $n$ ambulances). Quadrupling the size of the city
+increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
+and the number of ambulances increases proportionally).
+
+Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
+except with a much lower time complexity of $O(n) = n^2k$.
 

### 2013-11-16 LaTeX/paper.tex
Added steps 5, 4, 3 and 2 in part 1; working in reverse order

@@
 \begin{enumerate}
-    \item
-        The travel times given are calculated from an optimal route from the center of the first
+    \item The travel times given are calculated from an optimal route from the center of the first
         zone to the center of ths econd. This excludes the possibility of reaching a zone faster
         via an indirect route from the direct, given one.
-    \item
-        The travel times given for travel from any zone to itself is the average
+    \item The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item
-        The ratio between the time it takes inside a zone to travel toward a second zone,
+    \item The ratio between the time it takes inside a zone to travel toward a second zone,
         to the time it takes inside a zone to return from a second, is equal to the ratio
@@
     \item
-        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
+        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
         that multiple ambulances will cover different areas of the zones, thus evening out coverage.
-        (If partial coverages from multiple ambulances sum to above the total population of a zone,
-        we assume that zone is completely covered by the ambulances.)
 \end{enumerate}
@@
 
-\subsection{Part 1?}
+\subsection{Zone-to-Zone Population Dynamics}
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
@@
 zone-to-zone coverage.
+\begin{description}
+    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
+    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
+    \item[$v$] required ambulance response time
+    \item[$T_{AB}$] travel time from A to B, given
+    \item[$T_{BA}$] travel time from B to A, given
+    \item[$P_B$] total population of B
+    \item[$F_B(s)$] the probability curve for differences in travel time within B
+    \item[$T_{A^+}$] travel time inside of A traveling away from B
+    \item[$T_{A^-}$] travel time inside of A traveling toward B
+    \item[$T_{B^+}$] travel time inside of B traveling away from A
+    \item[$T_{B^-}$] travel time inside of B traveling toward A
+    \item[$a, b$] width of A and B respectively
+    \item[$g$] width of the gap between A and B
+\end{description}
 
-\subsection{Ambulance Distributon Optimization}
-Once the zone-to-zone coverages have been calculated, we must still decide where to place
-the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
-of the individual zones, i.e. the number of people that can be reached by at least one ambulance
-within eight minutes.
+%TODO: Graphical representation of origin and setup
 
-Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
-zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
-coverage.
+The function for zone-to-zone coverage in respect to travel time can be written out as 
+$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
+In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
+This is the average difference in travel time, and is equal to $T_{B+}$.
+$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
 
-Under the given conditions, we can easily find the optimal ambulance placement using a brute force
-method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
-However, this solution is not scalable to larger cities, as the brute force method has time complexity
-$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
-becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
-and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
-coverages for each of the $n$ ambulances). Quadrupling the size of the city
-increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
-and the number of ambulances increases proportionally).
-
-Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
-except with a much lower time complexity of $O(n) = n^2k$.
+\subsection{Ambulance Distributor}
+Once the zone-to-zone coverages have been
 

### 2013-11-16 LaTeX/paper.tex

--- 2013-11-16 LaTeX/paper.tex
@@
     \item[$P_B$] total population of B
+    \item[$F_B(s)$] the probability curve for differences in travel time within B
     \item[$T_{A^+}$] travel time inside of A traveling away from B
@@
 %TODO: Graphical representation of origin and setup
+
 The function for zone-to-zone coverage in respect to travel time can be written out as 
-$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
+$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
+In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
+This is the average difference in travel time, and is equal to $T_{B+}$.
+$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
 

### 2013-11-16 LaTeX/paper.tex

@@
 
-\subsection{Zone-to-Zone Population Dynamics}
+\subsection{Part 1?}
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
@@
     \item[$P_B$] total population of B
-    \item[$F_B(s)$] the probability curve for differences in travel time within B
     \item[$T_{A^+}$] travel time inside of A traveling away from B
@@
 %TODO: Graphical representation of origin and setup
+The function for zone-to-zone coverage in respect to travel time can be written out as 
+$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
 
-The function for zone-to-zone coverage in respect to travel time can be written out as 
-$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
-In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
-This is the average difference in travel time, and is equal to $T_{B+}$.
-$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
+\subsection{Ambulance Distributon Optimization}
+Once the zone-to-zone coverages have been calculated, we must still decide where to place
+the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
+of the individual zones, i.e. the number of people that can be reached by at least one ambulance
+within eight minutes.
 
-\subsection{Ambulance Distributor}
-Once the zone-to-zone coverages have been
+Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
+zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
+coverage.
+
+Under the given conditions, we can easily find the optimal ambulance placement using a brute force
+method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
+However, this solution is not scalable to larger cities, as the brute force method has time complexity
+$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
+becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
+and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
+coverages for each of the $n$ ambulances). Quadrupling the size of the city
+increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
+and the number of ambulances increases proportionally).
+
+Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
+except with a much lower time complexity of $O(n) = n^2k$.
 

### 2013-11-16 LaTeX/paper.tex
Refactoring assumptions/justifications

--- 2013-11-16 LaTeX/paper.tex
@@
 \section{Assumptions and Justifications}
-\begin{enumerate}
-    \item The travel times given are calculated from an optimal route from the center of the first
-        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
+\begin{description}
+    \item[1. Zone to Zone Travel] \hfill \\
+    	The travel times given are calculated from an optimal route from the center of the first
+        zone to the center of the second. This excludes the possibility of reaching a zone faster
         via an indirect route from the direct, given one.
-    \item The travel times given for travel from any zone to itself is the average
+    \item[2. Zone Interior Travel] \hfill \\
+    	The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item The ratio between the time it takes inside a zone to travel toward a second zone,
+    \item[3. Zone Directional Travel] \hfill \\
+    	The ratio between the time it takes inside a zone to travel toward a second zone,
         to the time it takes inside a zone to return from a second, is equal to the ratio
@@
         second to the first.
-    \item
+    \item[4. Ambulance Placement] \hfill \\
         Ambulances can only be placed in the very center of a zone. Because we do not know the
@@
         being closer to one zone or another.
-    \item
-        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
+    \item[5. Partial Coverage] \hfill \\
+        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
         that multiple ambulances will cover different areas of the zones, thus evening out coverage.
-\end{enumerate}
+\end{description}
 
@@
 %TODO: Graphical representation of origin and setup
-
 The function for zone-to-zone coverage in respect to travel time can be written out as 
-$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
-In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
-This is the average difference in travel time, and is equal to $T_{B+}$.
-$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
+$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
 

### 2013-11-16 LaTeX/paper.tex
Fixing detached head

--- 2013-11-16 LaTeX/paper.tex
@@
 \section{Assumptions and Justifications}
-\begin{enumerate}
-    \item
+\begin{description}
+    \item[1. Zone to Zone Travel] \hfill \\
     	The travel times given are calculated from an optimal route from the center of the first
-        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
+        zone to the center of the second. This excludes the possibility of reaching a zone faster
         via an indirect route from the direct, given one.
-    \item
+    \item[2. Zone Interior Travel] \hfill \\
     	The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item
+    \item[3. Zone Directional Travel] \hfill \\
     	The ratio between the time it takes inside a zone to travel toward a second zone,
@@
         being closer to one zone or another.
-    \item
-        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
+    \item[5. Partial Coverage] \hfill \\
+        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
-        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
-        (If partial coverages from multiple ambulances sum to above the total population of a zone,
+        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
         we assume that zone is completely covered by the ambulances.)
-\end{enumerate}
+\end{description}
 

### 2013-11-16 LaTeX/paper.tex
Refactoring Extensions

@@
 
-Even after our greedy algorithm reduces the overall solution time to an $O(n^2)$, or polynomial time, there are still possible ways to improve it.
+Even after our greedy algorithm reduces the overall solution time to an $O(n) = O(n^2k)$, or polynomial time, there are still possible ways to improve it.
 One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together.
-As a result of such a method, we would reduce the problem to one with an $O(nlog(n))$, an algorithm that would easily scale to larger data sets.
+As a result of such a method, we would reduce the problem to one with an $O(n) = O(nlog(n))$, an algorithm that would easily scale to larger data sets.
 

### 2013-11-16 LaTeX/paper.tex
Actually refactoring extensions

--- 2013-11-16 LaTeX/paper.tex
@@
 
-Even after our greedy algorithm reduces the overall solution time to an $O(n^2)$, or polynomial time, there are still possible ways to improve it.
+Even after our greedy algorithm reduces the overall solution time to an $O(n) = n^2k$, or polynomial time, there are still possible ways to improve it.
 One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together.
-As a result of such a method, we would reduce the problem to one with an $O(nlog(n))$, an algorithm that would easily scale to larger data sets.
+As a result of such a method, we would reduce the problem to one with an $O(n) = nlog(n)$, an algorithm that would easily scale to larger data sets.
 

### 2013-11-16 LaTeX/paper.tex
Added Step 1

--- 2013-11-16 LaTeX/paper.tex
@@
 \section{Assumptions and Justifications}
-\begin{description}
-    \item[1. Zone to Zone Travel] \hfill \\
-    	The travel times given are calculated from an optimal route from the center of the first
-        zone to the center of the second. This excludes the possibility of reaching a zone faster
+\begin{enumerate}
+    \item The travel times given are calculated from an optimal route from the center of the first
+        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
         via an indirect route from the direct, given one.
-    \item[2. Zone Interior Travel] \hfill \\
-    	The travel times given for travel from any zone to itself is the average
+    \item The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item[3. Zone Directional Travel] \hfill \\
-    	The ratio between the time it takes inside a zone to travel toward a second zone,
+    \item The ratio between the time it takes inside a zone to travel toward a second zone,
         to the time it takes inside a zone to return from a second, is equal to the ratio
@@
         second to the first.
-    \item[4. Ambulance Placement] \hfill \\
+    \item
         Ambulances can only be placed in the very center of a zone. Because we do not know the
@@
         being closer to one zone or another.
-    \item[5. Partial Coverage] \hfill \\
-        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
+    \item
+        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
-        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
-        we assume that zone is completely covered by the ambulances.)
-\end{description}
+        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
+\end{enumerate}
 
@@
     \item[$F_B(s)$] the probability curve for differences in travel time within B
-    \item[$T_{A^+}$] travel time inside of A traveling away from B
-    \item[$T_{A^-}$] travel time inside of A traveling toward B
-    \item[$T_{B^+}$] travel time inside of B traveling away from A
-    \item[$T_{B^-}$] travel time inside of B traveling toward A
+    \item[$T_{A+}$] average travel time in the direction of B to A inside of A
+    \item[$T_{A-}$] average travel time in the direction of A to B inside of A
+    \item[$T_{B+}$] average travel time in the direction of A to B inside of B
+    \item[$T_{B-}$] average travel time in the direction of B to A inside of B
     \item[$a, b$] width of A and B respectively
@@
 This is the average difference in travel time, and is equal to $T_{B+}$.
-$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
+$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
+The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
+$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
+The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out
 
-\subsection{Ambulance Distributon Optimization}
-Once the zone-to-zone coverages have been calculated, we must still decide where to place
-the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
-of the individual zones, i.e. the number of people that can be reached by at least one ambulance
-within eight minutes.
+the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal
 
-Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
-zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
-coverage.
-
-Under the given conditions, we can easily find the optimal ambulance placement using a brute force
-method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
-However, this solution is not scalable to larger cities, as the brute force method has time complexity
-$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
-becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
-and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
-coverages for each of the $n$ ambulances). Quadrupling the size of the city
-increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
-and the number of ambulances increases proportionally).
-
-Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
-except with a much lower time complexity of $O(n) = n^2k$.
+\subsection{Ambulance Distributor}
+Once the zone-to-zone coverages have been
 

### 2013-11-16 LaTeX/paper.tex
Fix typos.
Test Plan:
n/a

--- 2013-11-16 LaTeX/paper.tex
@@
     \item[5. Partial Coverage] \hfill \\
-        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
+        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
@@
 \begin{description}
-    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
-    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
-    \item[$v$] required ambulance response time
-    \item[$T_{AB}$] travel time from A to B, given
-    \item[$T_{BA}$] travel time from B to A, given
-    \item[$P_B$] total population of B
-    \item[$F_B(s)$] the probability curve for differences in travel time within B
-    \item[$T_{A^+}$] travel time inside of A traveling away from B
-    \item[$T_{A^-}$] travel time inside of A traveling toward B
-    \item[$T_{B^+}$] travel time inside of B traveling away from A
-    \item[$T_{B^-}$] travel time inside of B traveling toward A
-    \item[$a, b$] width of A and B respectively
-    \item[$g$] width of the gap between A and B
+    \item[$\mathbf{A(t), B(t)}$] \hfill \\
+    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
+    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
+    	Zone-to-zone coverage of B from A
+    \item[$\mathbf{v}$] \hfill \\
+    	Required ambulance response time
+    \item[$\mathbf{T_{AB}}$] \hfill \\
+    	Travel time from A to B, given
+    \item[$\mathbf{T_{BA}}$] \hfill \\
+    	Travel time from B to A, given
+    \item[$\mathbf{P_B}$] \hfill \\
+    	Total population of B
+    \item[$\mathbf{F_B(s)}$] \hfill \\
+    	The probability curve for differences in travel time within B
+    \item[$\mathbf{T_{A+}}$] \hfill \\
+    	Average travel time in the direction of B to A inside of A
+    \item[$\mathbf{T_{A-}}$] \hfill \\
+    	Average travel time in the direction of A to B inside of A
+    \item[$\mathbf{T_{B+}}$] \hfill \\
+    	Average travel time in the direction of A to B inside of B
+    \item[$\mathbf{T_{B-}}$] \hfill \\
+    	Average travel time in the direction of B to A inside of B
+    \item[$\mathbf{a, b}$] \hfill \\
+    	Width of A and B respectively
+    \item[$\mathbf{g}$] \hfill \\
+    	Width of the gap between A and B
 \end{description}
@@
 This is the average difference in travel time, and is equal to $T_{B+}$.
-$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$
+$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
+The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
+$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
+The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out
+
+the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal
 

### 2013-11-16 LaTeX/paper.tex
Refactoring variables
Added more words

@@
     \item[$F_B(s)$] the probability curve for differences in travel time within B
+    \item[$T_A$] average travel time inside of A
     \item[$T_{A+}$] average travel time in the direction of B to A inside of A
     \item[$T_{A-}$] average travel time in the direction of A to B inside of A
+    \item[$T_B$] average travel time inside of B
     \item[$T_{B+}$] average travel time in the direction of A to B inside of B
@@
 $$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
-The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out
-
-the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal
+The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
+$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
+We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
+$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$
 

### 2013-11-16 LaTeX/paper.tex
Fixing syntax

--- 2013-11-16 LaTeX/paper.tex
@@
 \begin{description}
+
     \item[$\mathbf{A(t), B(t)}$] \hfill \\
@@
     	The probability curve for differences in travel time within B
+   \item[$\mathbf{T_A}$] \hfill \\
+    	Average travel time inside of A
     \item[$\mathbf{T_{A+}}$] \hfill \\
@@
     	Average travel time in the direction of A to B inside of A
+   \item[$\mathbf{T_B}$] \hfill \\
+    	Average travel time inside of B
     \item[$\mathbf{T_{B+}}$] \hfill \\

### 2013-11-16 LaTeX/paper.tex
Assumption changes

@@
 \usepackage{caption}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \usepackage{fancyhdr}
@@
 
-% \pagestyle{fancy}
-% \lhead{Team 4552}
-% \chead{Problem A}
-% \rhead{}
+\pagestyle{fancy}
+\lhead{Team 4552}
+\chead{Problem A}
+\rhead{\thepage}
 
-% \renewcommand{\headrulewidth}{0.8pt}
-% \renewcommand{\footrulewidth}{0.8pt}
+\renewcommand{\headrulewidth}{.8pt}
+%\renewcommand{\footrulewidth}{.8pt}
 
@@
 \section{Problem Restatement}
-Given a fictitious district made up of six separate zones, and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
+Given a district made up of six separate zones and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
 Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.
 
-Then, consider a scenario in which a large scale disaster affects a single location (i.e.
-9/11), and discuss how an Emergency Service Coordinator would cover the situation.
-Examine how a real-world city or county would prepare for such a disaster.
+Then, consider a scenario in which a large scale disaster affects a single location (e.g.
+the September 11th attacks), and discuss how an Emergency Service Coordinator would cover the situation.
+Examine how a real-world city or district would prepare for such a disaster.
 Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.
@@
 \begin{description}
-    \item[1. Zone to Zone Travel] \hfill \\
+    \item[1. Naming] \hfill \\
+    	A district is another name for a county. ...
+    \item[2. Zone to Zone Travel] \hfill \\
     	The travel times given are calculated from an optimal route from the center of the first
@@
         via an indirect route from the direct, given one.
-    \item[2. Zone Interior Travel] \hfill \\
+    \item[3. Travel Inside Each Zone] \hfill \\
     	The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item[3. Zone Directional Travel] \hfill \\
+    \item[4. Directional Travel Inside Each Zone] \hfill \\
     	The ratio between the time it takes inside a zone to travel toward a second zone,
@@
         second to the first.
-    \item[4. Ambulance Placement] \hfill \\
+    \item[5. Ambulance Placement] \hfill \\
         Ambulances can only be placed in the very center of a zone. Because we do not know the
@@
         being closer to one zone or another.
-    \item[5. Partial Coverage] \hfill \\
+    \item[6. Partial Coverage] \hfill \\
         Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
@@
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
-zone-to-zone coverage.
+that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
 \begin{description}
-
     \item[$\mathbf{A(t), B(t)}$] \hfill \\
@@
 
-\subsection{Ambulance Distributon Optimization}
+\subsection{Ambulance Distribution Optimization}
 Once the zone-to-zone coverages have been calculated, we must still decide where to place
@@
 
-\subsection{3 Ambulance Cover}
+\subsection{The $n$ Ambulance Problem}
 
-\subsection{2 Ambulance Cover}
+\subsubsection{$n=3$ Problem}
 
-\subsection{1 Ambulance Cover}
+\subsubsection{$n=2$ Problem}
 
-\subsection{Catastrophic Cover}
+\subsubsection{$n=1$ Problem}
+
+\subsection{Localized Single Zone Disaster}
 In a localized catastrophic event such as those that happened on September 11, 2001, there will be

### 2013-11-16 LaTeX/paper.tex
Fixing Header/footer

--- 2013-11-16 LaTeX/paper.tex
@@
     \item[5. Partial Coverage] \hfill \\
-        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
+        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
@@
     	The probability curve for differences in travel time within B
-   \item[$\mathbf{T_A}$] \hfill \\
-    	Average travel time inside of A
     \item[$\mathbf{T_{A+}}$] \hfill \\
@@
     	Average travel time in the direction of A to B inside of A
-   \item[$\mathbf{T_B}$] \hfill \\
-    	Average travel time inside of B
     \item[$\mathbf{T_{B+}}$] \hfill \\
@@
 $$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
-The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
-$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
-We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
-$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$
+The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out
+
+the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal
 

### 2013-11-16 LaTeX/paper.tex

--- 2013-11-16 LaTeX/paper.tex
@@
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
-zone-to-zone coverage.
+that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
 \begin{description}

### 2013-11-16 LaTeX/paper.tex
More assumptions

--- 2013-11-16 LaTeX/paper.tex
@@
 \begin{description}
+    \item[TODO(drew): Add these assumptions] \hfill \\
+    	* Each zone is not a point, but rather a distribution. We experimented with...
+	* Route frequency is correlated with population frequency (two random variables?)
     \item[1. Naming] \hfill \\
-    	A district is another name for a county. ...
+    	A district is another name for a county. ... TODO(drew)
+	Travel...
     \item[2. Zone to Zone Travel] \hfill \\
-    	The travel times given are calculated from an optimal route from the center of the first
-        zone to the center of the second. This excludes the possibility of reaching a zone faster
-        via an indirect route from the direct, given one.
+    	The travel times given are considered to be optimal routes from the center of one zone to the center of the another, regardless of any other zones that may lie in between.
     \item[3. Travel Inside Each Zone] \hfill \\

### 2013-11-16 LaTeX/paper.tex
Added equations

--- 2013-11-16 LaTeX/paper.tex
@@
 \usepackage{caption}
-% \usepackage{fullpage}
+\usepackage{fullpage}
 \usepackage{fancyhdr}
@@
 
-\pagestyle{fancy}
-\lhead{Team 4552}
-\chead{Problem A}
-\rhead{\thepage}
+% \pagestyle{fancy}
+% \lhead{Team 4552}
+% \chead{Problem A}
+% \rhead{}
 
-\renewcommand{\headrulewidth}{.8pt}
-%\renewcommand{\footrulewidth}{.8pt}
+% \renewcommand{\headrulewidth}{0.8pt}
+% \renewcommand{\footrulewidth}{0.8pt}
 
@@
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
+that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
+zone-to-zone coverage.
 \begin{description}
@@
 $$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
+
 In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
@@
 $$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
+
 The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
 $$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
+
 The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
+We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
+The same can be done with $T_{B}$.
 $$T_A = \frac{T_{A+} + T_{A-}}{2}$$
-We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
 $$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$ 
+$$\frac{T_{B+}}{T_{B-}} = \frac{T_{AB}}{T_{BA}}$$
+
+This allows us to solve for $T_{A-}$  and $T_{B+}$.
+$$T_{A-} = \frac {2T_A}{1+ \frac{T_{BA}}{T_{AB}}}$$
+$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}}$$
 
@@
 
-\subsection{The $n$ Ambulance Problem}
+\subsection{3 Ambulance Cover}
 
-\subsubsection{$n=3$ Problem}
+\subsection{2 Ambulance Cover}
 
-\subsubsection{$n=2$ Problem}
+\subsection{1 Ambulance Cover}
 
-\subsubsection{$n=1$ Problem}
-
-\subsection{Localized Single Zone Disaster}
+\subsection{Catastrophic Cover}
 In a localized catastrophic event such as those that happened on September 11, 2001, there will be

### 2013-11-16 LaTeX/paper.tex
Adding bibliography

--- 2013-11-16 LaTeX/paper.tex
@@
 \section{Problem Restatement}
-Given a district made up of six separate zones and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
+Given a fictitious district made up of six separate zones, and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
 Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.
 
-Then, consider a scenario in which a large scale disaster affects a single location (e.g.
-the September 11th attacks), and discuss how an Emergency Service Coordinator would cover the situation.
-Examine how a real-world city or district would prepare for such a disaster.
+Then, consider a scenario in which a large scale disaster affects a single location (i.e.
+9/11), and discuss how an Emergency Service Coordinator would cover the situation.
+Examine how a real-world city or county would prepare for such a disaster.
 Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.
@@
 \begin{description}
-    \item[TODO(drew): Add these assumptions] \hfill \\
-    	* Each zone is not a point, but rather a distribution. We experimented with...
-	* Route frequency is correlated with population frequency (two random variables?)
-    \item[1. Naming] \hfill \\
-    	A district is another name for a county. ... TODO(drew)
-	Travel...
-    \item[2. Zone to Zone Travel] \hfill \\
-    	The travel times given are considered to be optimal routes from the center of one zone to the center of the another, regardless of any other zones that may lie in between.
-    \item[3. Travel Inside Each Zone] \hfill \\
+    \item[1. Zone to Zone Travel] \hfill \\
+    	The travel times given are calculated from an optimal route from the center of the first
+        zone to the center of the second. This excludes the possibility of reaching a zone faster
+        via an indirect route from the direct, given one.
+    \item[2. Zone Interior Travel] \hfill \\
     	The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item[4. Directional Travel Inside Each Zone] \hfill \\
+    \item[3. Zone Directional Travel] \hfill \\
     	The ratio between the time it takes inside a zone to travel toward a second zone,
@@
         second to the first.
-    \item[5. Ambulance Placement] \hfill \\
+    \item[4. Ambulance Placement] \hfill \\
         Ambulances can only be placed in the very center of a zone. Because we do not know the
@@
         being closer to one zone or another.
-    \item[6. Partial Coverage] \hfill \\
+    \item[5. Partial Coverage] \hfill \\
         Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
@@
 
-\subsection{Ambulance Distribution Optimization}
+\subsection{Ambulance Distributon Optimization}
 Once the zone-to-zone coverages have been calculated, we must still decide where to place
@@
 such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
-injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
+injured first, who will be sorted by triage \cite{ColRev}. Therefore, it is very important for ambulances to be able to
 reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
@@
 
-\bibliographystyle{chicago}
-\bibliography{bibliography}
+\bibliographystyle{unsrt}
+\bibliography{references}
 \end{document}

### 2013-11-16 LaTeX/paper.tex
error fixing

@@
 However, this solution is not scalable to larger cities, as the brute force method has time complexity
-$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
-becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
+$O(n, k) = nk\binom{k}{n}$ where $k$ is the number of zones to cover, and $n$ is the number of ambulances to place, which
+becomes intractable as $n$ and $k$ increase (since it has to check $\binom{k}{n}$ placements,
 and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
@@
 Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
-except with a much lower time complexity of $O(n) = n^2k$.
+except with a much lower time complexity of $O(n, k) = n k^2$.
 
@@
 With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is not a pressing issue.
-As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligent amount of time.
+As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligible amount of time.
 However, as we look to expanding the model to fit a larger area, with more zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.
 
-Even after our greedy algorithm reduces the overall solution time to an $O(n) = n^2k$, or polynomial time, there are still possible ways to improve it.
+Even after our greedy algorithm reduces the overall solution time to an $O(n, k) = nk^2$, or polynomial time, there are still possible ways to improve it.
 One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together.
-As a result of such a method, we would reduce the problem to one with an $O(n) = nlog(n)$, an algorithm that would easily scale to larger data sets.
+As a result of such a method, we would reduce the problem to one with an $O(n, k) = nk\log(k)$, an algorithm that would easily scale to larger data sets.
 
@@
 
-\item Allocate $n$ ambulances across each subdistrict.
-If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance)
+\item Allocate $n$ ambulances across the subdistricts.
+If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance).
 
-\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole
+\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole.
 \end{enumerate}

### 2013-11-16 LaTeX/paper.tex
formatting
further progress on ambulance distribution

@@
 
-\title{\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}}
+\title{\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}}
 \author{Team 4552}
@@
 \section{Problem Restatement}
-Given a district made up of six separate zones and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
-Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.
+Given a county made up of six separate zones and average travel times between zones, create a model
+to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an
+eight minute period. Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for
+each scenario, keep track of how many people are not being reached with each possible solution.
 
-Then, consider a scenario in which a large scale disaster affects a single location (e.g.
-the September 11th attacks), and discuss how an Emergency Service Coordinator would cover the situation.
-Examine how a real-world city or district would prepare for such a disaster.
-Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.
+Then, consider a scenario in which a large scale disaster affects a single location (e.g. the September 11th attacks),
+and discuss how an Emergency Service Coordinator would cover the situation. Examine how a real-world city or
+county would prepare for such a disaster. Finally, write a two page memo detailing the model and its analysis
+for the Emergency Service Coordinator.
 
@@
     \item[1. Naming] \hfill \\
-    	A district is another name for a county. ... TODO(drew)
+    	A county is another name for a county. ... TODO(drew)
         Travel...
     \item[2. Zone to Zone Travel] \hfill \\
-    	The travel times given are considered to be optimal routes from the center of one zone to the center of the another, regardless of any other zones that may lie in between.
+    	The travel times given are considered to be optimal routes from the center of one zone to
+        the center of the another, regardless of any other zones that may lie in between.
     \item[3. Travel Inside Each Zone] \hfill \\
@@
         zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
-        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
+        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
+        (If partial coverages from multiple ambulances sum to above the total population of a zone,
         we assume that zone is completely covered by the ambulances.)
@@
 An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
+that the ambulance can cover in a second zone from a first zone (not necessarily distinct),
+will be hereafter referred to as zone-to-zone coverage.
 \begin{description}
@@
 
-In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B.
-This is the average difference in travel time, and is equal to $T_{B+}$.
+In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B,
+$F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$.
 $$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
 
-The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
+The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation
+of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
 $$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
 
-The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
-We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
-The same can be done with $T_{B}$.
+The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A
+inside of A, $T_{A+}$, have a total average travel time of $T_A$. We can also write the ratio of $T_{A+}$ and $T_{A-}$,
+which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$. The same can be done with $T_{B}$.
 $$T_A = \frac{T_{A+} + T_{A-}}{2}$$
@@
 Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
-except with a much lower time complexity of $O(n, k) = n k^2$.
+except with a much lower time complexity of $O(n, k) = n k^2$. The greedy heuristic works by assigning ambulances to zones
+one at a time. For each assignment, we iterate through each zone without an ambulance already assigned, and see how many
+additional people it would cover; then we assign an ambulance to the zone which would most increase the number of
+covered people.
 
@@
 \section{Extensions}
-Though our model performs fairly well already, providing us with the optimal locations of our $n$ ambulances to maximize the number of people saved, there are a number of ways we can improve the model so that we can make more accurate predictions as to the number of people we can reach in an eight minute period.
-Furthermore, we can also improve the overall efficiency of the solution algorithm itself, by looking at potential dynamic programming approaches to the problem.
+Though our model performs fairly well already, providing us with the optimal locations of our $n$ ambulances to
+maximize the number of people saved, there are a number of ways we can improve the model so that we can make more
+accurate predictions as to the number of people we can reach in an eight minute period. Furthermore, we can also
+improve the overall efficiency of the solution algorithm itself, by looking at potential dynamic programming approaches to the problem.
 
-While any algorithmic changes may not be necessary with only six zones, and a maximum of $n = 3$ ambulances, if we scale this problem up to a large city, or across multiple counties, algorithm efficiency becomes an important problem that requires attention.
+While any algorithmic changes may not be necessary with only six zones, and a maximum of $n = 3$ ambulances, if
+we scale this problem up to a large city, or across multiple counties, algorithm efficiency becomes an important problem that requires attention.
 
 \subsection{Population Distribution}
-As it currently stands, we have very little information regarding the actual population distribution of each zone in the scope of the district, which provides us with a slightly skewed perception.
-While we justified the use of a standard distribution for population above, we have the ability to greatly improve our model with a better idea of how spread out a population of a zone actually is, in relation to its epicenter.
-This information allows us to better predict how many people an ambulance would miss (not be able to cover) in a certain zone.
+As it currently stands, we have very little information regarding the actual population distribution of each
+zone in the scope of the county, which provides us with a slightly skewed perception. While we justified the
+use of a standard distribution for population above, we have the ability to greatly improve our model with a
+better idea of how spread out a population of a zone actually is, in relation to its epicenter. This information
+allows us to better predict how many people an ambulance would miss (not be able to cover) in a certain zone.
 
-The number of missed people is an important statistic that an Emergency Service Coordinator needs to have in order to fully optimize their resources.
-In our system now, we predict this number with a certain level of accuracy, but we are still prone to a relatively large amount of error.
-With a better understanding of the population and geospacial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.
+The number of missed people is an important statistic that an Emergency Service Coordinator needs to have in
+order to fully optimize their resources. In our system now, we predict this number with a certain level of accuracy,
+but we are still prone to a relatively large amount of error. With a better understanding of the population and
+geospacial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.
 
 \subsection{Dynamic Approach}
-With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is not a pressing issue.
-As we have shown above, even a brute force attempt at optimizing the ambulance locations takes a negligible amount of time.
-However, as we look to expanding the model to fit a larger area, with more zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.
+With only a total of six zones and a maximum of $n = 3$ ambulances to allocate, overall algorithm efficiency is
+not a pressing issue. As we have shown above, even a brute force attempt at optimizing the ambulance locations
+takes a negligible amount of time. However, as we look to expanding the model to fit a larger area, with more
+zones, and more ambulances, it becomes increasingly more important to look for ways to make our algorithm more efficient.
 
-Even after our greedy algorithm reduces the overall solution time to an $O(n, k) = nk^2$, or polynomial time, there are still possible ways to improve it.
-One such method would be the use of dynamic programming methods to split the problem up into a series of smaller subproblems, and then merge the results together.
-As a result of such a method, we would reduce the problem to one with an $O(n, k) = nk\log(k)$, an algorithm that would easily scale to larger data sets.
+Even after our greedy algorithm reduces the overall solution time to an $O(n, k) = nk^2$, or polynomial time, there
+are still possible ways to improve it. One such method would be the use of dynamic programming methods to split the
+problem up into a series of smaller subproblems, and then merge the results together. As a result of such a method,
+we would reduce the problem to one with an $O(n, k) = nk\log(k)$, an algorithm that would easily scale to larger data sets.
 
-However, the implementation of such a method is slightly less simple. One such way to implement a solution in this manner would be in the following fashion:
+However, the implementation of such a method is slightly less simple.
+One such way to implement a solution in this manner would be in the following fashion:
 
 \begin{enumerate}
-\item Given a graph of each node (zone), and the edges between them (time it takes to travel between nodes), immediately remove all infeasible edges, with edge length (time) greater than the eight minute baseline.
+\item Given a graph of each node (zone), and the edges between them (time it takes to travel between nodes),
+    immediately remove all infeasible edges, with edge length (time) greater than the eight minute baseline.
 
-\item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential split points, to divide each district into smaller subdistricts.
-Make sure to account for overlap.
+\item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential
+    split points, to divide each county into smaller subcounties. Make sure to account for overlap.
 
-\item Allocate $n$ ambulances across the subdistricts.
-If there are fewer ambulances than are necessary to cover the entire district, weight each subdistrict by population size (save more people per ambulance).
+\item Allocate $n$ ambulances across the subcounties. If there are fewer ambulances than are necessary to cover
+    the entire county, weight each subcounty by population size (save more people per ambulance).
 
-\item Solve each subdistrict for the optimal ambulance location, thereby finding a solution for the set as a whole.
+\item Solve each subcounty for the optimal ambulance location, thereby finding a solution for the set as a whole.
 \end{enumerate}
 
-While we are not guaranteed to find the optimal solution to ambulance location, we will be provided with a relatively good one, in a short amount of time.
-There are tradeoffs to using such a model, but especially at a large scale, this methodology is realistically the one an Emergency Service Coordinator would use.
+While we are not guaranteed to find the optimal solution to ambulance location, we will be provided with a relatively
+good one, in a short amount of time. There are tradeoffs to using such a model, but especially at a large scale,
+this methodology is realistically the one an Emergency Service Coordinator would use.
 

### 2013-11-16 LaTeX/paper.tex
Working hard

@@
 \subsection{The $n$ Ambulance Problem}
+With the $n$ ambulance problem, we are trying to figure out where to place each of the $n$ ambulances so that the reach of each ambulance covers the most amount of people.
+For our purposes, this reach is solely determined by how far the ambulance can travel in an eight minute span.
 
-\subsubsection{$n=3$ Problem}
+With the given county, made up of six zones, we consider the location optimization under three scenarios; with three ambulances, with two ambulances, and finally, with one ambulance.
+Our goal is to see a) if we can cover everybody in the county in an eight minute span, and b) if not, how many people are we failing to cover.
 
-\subsubsection{$n=2$ Problem}
+The number of people the ambulances are able to cover is a function of our population density function, while the actual location optimization is done by our greedy optimizer.
 
-\subsubsection{$n=1$ Problem}
+\subsubsection{$n=3$}
+
+\subsubsection{$n=2$}
+
+\subsubsection{$n=1$}
 

### 2013-11-16 LaTeX/paper.tex
Add model approach.

@@
 \section{Problem Restatement}
-Given a county made up of six separate zones and average travel times between zones, create a model
-to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an
-eight minute period. Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for
-each scenario, keep track of how many people are not being reached with each possible solution.
+Given a county made up of six separate zones and average travel times between zones, create a model to optimize the placement of $n$ ambulances in order to maximize the number of civilians reached in an eight minute period.
+Consider the scenarios where $n = 3$, $n = 2$, and $n = 1$, respectively, and for each scenario, keep track of how many people are not being reached with each possible solution.
 
-Then, consider a scenario in which a large scale disaster affects a single location (e.g. the September 11th attacks),
-and discuss how an Emergency Service Coordinator would cover the situation. Examine how a real-world city or
-county would prepare for such a disaster. Finally, write a two page memo detailing the model and its analysis
-for the Emergency Service Coordinator.
+Then, consider a scenario in which a large scale disaster affects a single location (e.g.
+the September 11th attacks), and discuss how an Emergency Service Coordinator would cover the situation.
+Examine how a real-world city or county would prepare for such a disaster.
+Finally, write a two page memo detailing the model and its analysis for the Emergency Service Coordinator.
 
@@
 
+Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who be reached in eight minutes or fewer.
+This system can be represented as a graph of $n$ and $k$ vertices.
+By analyzing all possible configurations, we can identify the ideal nodes to place the ambulances.
+This algorithm can be made more efficient---albeit less optimal---by employing a greedy heuristic that only focuses on the nodes that provide the most added coverage.
+
+Each zone is a region, and therefore the population is not concentrated on one point.
+As a result, ambulances will often be able to cover only a fraction of a zone's total population.
+In order to find these fractions, we developed a model of population density for each zone by extrapolating from the provided average travel times between zones.
+
+Travel time from a zone A to another zone B is not necessarily the same as the travel time in the opposite direction.
+This inconsistency could be due to a variety of factors, including differences in traffic, roads, and conditions.
+As a result, these two cases for each pair of zones must be handled separately.
+
 \subsection{Zone-to-Zone Population Dynamics}
@@
 will be hereafter referred to as zone-to-zone coverage.
+
+A lack of spatial understanding of the county entails the use of a different type of population density.
+Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point.
+This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.
+
+The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
+
 \begin{description}
@@
 but we are still prone to a relatively large amount of error. With a better understanding of the population and
-geospacial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.
+geospatial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.
 
@@
 \item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential
-    split points, to divide each county into smaller subcounties. Make sure to account for overlap.
+    split points, to divide each county into smaller sub-counties. Make sure to account for overlap.
 
-\item Allocate $n$ ambulances across the subcounties. If there are fewer ambulances than are necessary to cover
-    the entire county, weight each subcounty by population size (save more people per ambulance).
+\item Allocate $n$ ambulances across the sub-counties. If there are fewer ambulances than are necessary to cover
+    the entire county, weight each sub-county by population size (save more people per ambulance).
 
-\item Solve each subcounty for the optimal ambulance location, thereby finding a solution for the set as a whole.
+\item Solve each sub-county for the optimal ambulance location, thereby finding a solution for the set as a whole.
 \end{enumerate}

### 2013-11-16 Code/optimizer.py
added code stuffs

@@ -27,17 +27,10 @@ class const_curve(Function):
     def eval(cls, a, x):
         return 1 / a
 
+PROB_CURVE = const_curve  # selected model for population distribution
 
-class gauss_curve(Function):
-    nargs = 2
-
-    @classmethod
-    def eval(cls, a, x):
-        return 0  # TODO
-
-PROB_CURVE = quad_curve  # selected model for population distribution
-
-expected_value = integrate(integrate(PROB_CURVE(a, t) * PROB_CURVE(a, t - s), (t, -a / 2, a / 2)) * s, (s, 0, a))
+expected_value = integrate(integrate(PROB_CURVE(a, t) * PROB_CURVE(a, t - s),
+                                     (t, -a / 2, a / 2)) * s, (s, 0, a))
 # integral that should equal t_bbp
 
 
@@ -54,7 +47,8 @@ def calc_cover(start, target):
     b_end = min(b / 2, MAX_TIME - t_ab)
     if b_start > b_end:
         return 0
-    return round(integrate(PROB_CURVE(b, t), (t, b_start, b_end)) * populations[target])
+    return int(integrate(PROB_CURVE(b, t), (t, b_start, b_end)) *
+               populations[target], round='standard')
 
 
 for i in xrange(NODES):
@@ -78,16 +72,18 @@ def greedyoptimize(nambulances):
                 continue  # don't duplicate zones
             coverage = 0
             for target in xrange(NODES):
-                # additional coverage will increase the coverage to, at most
-                # the population of the zone
-                coverage += min(zz_coverage[start, target], populations[target] - covered[target])
+                # additional coverage will increase the coverage to,
+                # at most the population of the zone
+                coverage += min(zz_coverage[start, target],
+                                populations[target] - covered[target])
             if coverage > maxcoverage:
                 maxcoverage = coverage
                 bestnode = start
         startnodes.append(bestnode)
         for target in xrange(NODES):
-            covered[target] += min(zz_coverage[bestnode, target], populations[target] - covered[target])
-    return (startnodes, covered)
+            covered[target] += min(zz_coverage[bestnode, target],
+                                   populations[target] - covered[target])
+    return ([i + 1 for i in startnodes], covered)  # change 0 to 1-indexing
 
 
 def bruteforce(nambulances):
@@ -96,12 +92,14 @@ def bruteforce(nambulances):
     and arranges them so that there is maximum coverage among zones.
     '''
     maxcoverage = np.zeros(NODES)
[…]

### 2013-11-16 LaTeX/paper.tex
added code stuffs
add stuff about individual cases

@@
 \usepackage{setspace}
+\usepackage{minted}
+\usemintedstyle{colorful}
 \graphicspath{{./Pictures/}}
@@
 \subsubsection{$n=3$}
+We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
+2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
+zone 1.
 
 \subsubsection{$n=2$}
+We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
+2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
+zone 1, and none of zone 3.
 
 \subsubsection{$n=1$}
+We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.
 
@@
 \section{Strengths and Weaknesses}
+Our program is readily scalable to larger cities and larger numbers of ambulances, and due to using an
+efficient greedy heuristic it runs in polynomial time.
 
@@
 \section{Code}
+\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
 

### 2013-11-16 Code/optimizer.py

@@ -48,7 +48,7 @@ def calc_cover(start, target):
     if b_start > b_end:
         return 0
     return int(integrate(PROB_CURVE(b, t), (t, b_start, b_end)) *
-               populations[target], round='standard')
+               populations[target] + 0.5)
 
 
 for i in xrange(NODES):

### 2013-11-16 LaTeX/paper.tex
Updated Code Appendix
add figures

@@
 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=4in]{B(t).png}
+\caption{An example of a zone's population density as a function of travel time from another zone.}
+\label{B(t)}
+\end{center}
+\end{figure}
+
 The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
+
+\begin{figure}[htbp]
+\begin{center}
+
+\includegraphics[width=4in]{A(t)B(t).png}
+\caption{An2 example of a zone's population density as a function of travel time from another zone.}
+\label{A(t)B(t)}
+\end{center}
+\end{figure}
 
@@
 \section{Code}
+The following contains the code for both our brute force location optimizer, as well as the greedy optimizer.
+Both functions take a parameter $nambulances$, representing the total number of ambulances we have to allocate across the county.
+
 \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

### 2013-11-16 LaTeX/paper.tex
Fixing Strength and Weaknesses

@@
 \tableofcontents
-\newpage
+
 \section{Problem Restatement}
@@
 \section{Strengths and Weaknesses}
-Our program is readily scalable to larger cities and larger numbers of ambulances, and due to using an
-efficient greedy heuristic it runs in polynomial time.
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{ p{6.25cm}|p{6.25cm} }
+        \textbf{Strengths} & \textbf{Weaknesses}\\
+        \hline
+        1.
+Our model, by virtue of its polynomial-time greedy selection algorithm, is extremely scalable.
+We can scale up to large datasets, consisting of many, larger zones.
+Also, because of a non-exponential time algorithm, our model is also extremely efficient.
+& 1.
+Because of the greedy nature of our algorithm, we are not guaranteed to find the optimal solution for the location of the ambulances.\\
+        2.
+Our model is also adaptable to various different population distributions.
+Population Distributions can vary with the addition of any new data.
+The more accurate the data, the more accurate the model becomes.
+& 2.
+In order to find the optimal solution, our brute force optimizer works in exponential time, so at a large scale, finding the optimal placement of ambulances is near impossible.
+\\
+        3. Completely flexible model. Depending on any number of nodes, any number of ambulances, and any population distribution, we will be able to find a good answer relatively quickly.
+
+    \end{tabular}
+    \caption{Model Strengths \& Weaknesses}
+    \label{tab:modelprocons}
+\end{table}
 
@@
 
+\newpage
 \appendix

### 2013-11-16 LaTeX/paper.tex
Resized figures & stuff.
Hey Jude, don't let me down
Fixing merge conflicts
Fixing spacing bug
add the devil
Add 2nd devil image

@@
 \usepackage{setspace}
-\usepackage{minted}
-\usemintedstyle{colorful}
+% \usepackage{minted}
+% \usemintedstyle{colorful}
 \graphicspath{{./Pictures/}}
@@
 
-Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who be reached in eight minutes or fewer.
-This system can be represented as a graph of $n$ and $k$ vertices.
+Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who can be reached in eight minutes or fewer.
+This system can be represented as a graph of $n$ nodes and $n^2$ vertices.
 By analyzing all possible configurations, we can identify the ideal nodes to place the ambulances.
@@
 
+\begin{figure}
+\centering
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=0.9\linewidth]{B(t).png}
+  \caption{An example of a zone's population density as a function of travel time from another zone.}
+  \label{fig:sub1}
+\end{subfigure}%
+\hfill
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
+  \caption{TODO(drew)}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{Overarching caption whatever}
+\label{fig:test}
+\end{figure}
+
+The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
+\newpage
+
 \begin{figure}[htbp]
 \begin{center}
-\includegraphics[width=4in]{B(t).png}
-\caption{An example of a zone's population density as a function of travel time from another zone.}
-\label{B(t)}
+\includegraphics[width=3.5in]{A(t)B(t).png}
+\caption{TODO(drew)}
+\label{A(t)B(t)}
 \end{center}
@@
 
-The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3.5in]{6point.pdf}
+\caption{TODO(drew)}
+\label{A(t)B(t)}
+\end{center}
+\end{figure}
 
@@
 \begin{center}
-
-\includegraphics[width=4in]{A(t)B(t).png}
-\caption{An2 example of a zone's population density as a function of travel time from another zone.}
+\includegraphics[width=3.5in]{greedy6point.pdf}
+\caption{TODO(drew)}
 \label{A(t)B(t)}
@@
 
-\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
+% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
 

### 2013-11-16 LaTeX/paper.tex
Captioned figure & stuff

@@
 \end{subfigure}
-\caption{Overarching caption whatever}
 \label{fig:test}
@@
 \includegraphics[width=3.5in]{A(t)B(t).png}
-\caption{TODO(drew)}
-\label{A(t)B(t)}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{6point.pdf}
-\caption{TODO(drew)}
-\label{A(t)B(t)}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{greedy6point.pdf}
 \caption{TODO(drew)}
@@
 \subsubsection{$n=3$}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3in]{6point.pdf}
+\caption{Graph of zones, populations, and travel times}
+\end{center}
+\label{fig:fullgraph}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3in]{greedy6point.pdf}
+\caption{Graph as in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
+\end{center}
+\end{figure}
+
 We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones

### 2013-11-16 LaTeX/paper.tex
fixed figure ref
Bug fixes

@@
 \begin{figure}[htbp]
+\label{fig:fullgraph}
 \begin{center}
@@
 \end{center}
-\label{fig:fullgraph}
 \end{figure}
@@
 \includegraphics[width=3in]{greedy6point.pdf}
-\caption{Graph as in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
+\caption{Graph in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
 \end{center}
@@
 2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
-zone 1, and none of zone 3.
+zone 1, and half (28333/55000) of zone 3.
 
 \subsubsection{$n=1$}
-We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.
+We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 2.
+This arrangement allows the single ambulance to cover all of zone 2, half (25000/5000) of zone 1,
+and half (28333/55000) of zone 3.
+
+For all of these scenarios, our greedy heuristic got the exact same answer as the
+brute-force algorithm, guaranteeing an optimal answer, which indicates that our greedy heuristic
+is good. %TODO make sound good
 

### 2013-11-16 LaTeX/paper.tex
Adding to results

--- 2013-11-16 LaTeX/paper.tex
@@
 
-We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
-2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
-zone 1.
+Figure 2 above shows every possible route between zones, with their respective weight, or in this case, the time necessary to travel from one zone to another.
+For example, traveling from Zone 1 to Zone 6 would take 16 minutes, and vice versa.
+
+However, if you look at each of the routes, you see that some paths take longer than 8 minutes to travel.
+In this case, it would be impossible for an ambulance to make it from one zone to another in the necessary 8 minute time interval, and therefore, it would be impossible to save anyone along that route.
+
+In order to combat this, we look at Figure 3, above, which has significantly fewer paths.
+By eliminating the paths that require a travel time of more than 8 minutes, we have effectively cut our search time significantly, and allows to intuitively see some features of the graph.
+
+First and foremost, if you look at Zone 2, you see two paths going out to Zones 1 and 3, respectively.
+Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 5 is slightly larger, and you are more likely to save more people.
+Furthermore, the overall population density of the three zones (1+2+3) is large, weighing Zone 2 as one of the more important nodes on the graph.
+Therefore, intuitively, Zone 2 makes sense as a starting point.
+
+In the same way, if you look at Zone 5, you see two other paths going outwards to Zone 4 and Zone 6, respectively.
+Because neither of these two zones is represented with placing an ambulance in Zone 2, it follows that another ambulance should be placed in Zone 5, therefore covering the bulk of the county.
+
+Finally, if you look at Zone 3, you see that while though redundant, the overall population covered by having an ambulance stationed there is the next greatest.
+For that reason, it makes the most sense to place the third ambulance in Zone 3.
+
+Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 3 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes.
+Therefore, it shouldn't be surprising that when we ran the greedy algorithm for $n=3$ we got that ambulances should be placed in zones
+2, 5, and 3.
+When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of zone 1, accounting for a majority of the county.
 
 \subsubsection{$n=2$}
-We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
-2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
-zone 1, and none of zone 3.
+When we ran the greedy algorithm for $n=2$ we got that ambulances should be placed in zones
+2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half      (25000/50000) of zone 1, and none of zone 3.
 
 \subsubsection{$n=1$}
-We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.
+Finally, when we ran the greedy algorithm for $n=1$ we found that our ambulance should be placed in zone 2.
+This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.
 

### 2013-11-16 LaTeX/paper.tex
Cleaning up calvin's shit

@@
 This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.
+
+For each of these scenarios, our greedy heuristic got the exact same answer as the
+brute-force algorithm as well as the intuitive solution from the graph.
+Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing extremely efficiently and accurately.
 

### 2013-11-16 LaTeX/paper.tex
Putting in memo

@@
 
+\newpage
 \section{Non-Technical Memo}
+A county with a six zones needs to maximize the number of people that can be reached within eight minutes using its three ambulances.
+Given the average amount of time necessary to travel  between each of the zones, we must develop an algorithm for determining the optimal placement of the ambulances.
+
+In order to solve this problem, we first needed to develop a firm understanding of how many people a single ambulance can reach within eight minutes.
+In order to get an accurate representation of how many people an ambulance can actually reach, we took into account the fact that a zone is has an area and that the population of a zone is spread out over its entire area.
+While we assumed that the population density is linear, we designed our solution to be flexible enough to implement  any  symmetrical population distribution.
+
+Because distance in this scenario is unknown, we are forced to use another unit to represent the population density.
+Given that we want to travel from zone A to zone B, we chose to model the population density of zone B as a function of travel time from zone A.
+Using this function, we were able to calculate the time it would take to travel through all of B (the width) and the number of people covered in B per travel time away from A.
+By taking the number of people covered and the given travel times between each of the zones, we were able to calculate the theoretical number of people reachable within eight minutes by an ambulance for each zone.
+
+After calculating the maximum number of people coverable by one ambulance, we still need to figure out where we should put the ambulances to cover the most people.
+We approach this problem in two ways: we use a brute-force method, enumerating all possible combinations of ambulance positions, and picking the one that covered the most people; we also create a greedy heuristic, which doesn’t necessarily pick the optimal solution but runs much more quickly than the brute-force algorithm, and has proven to be very robust as well.
 

### 2013-11-16 LaTeX/paper.tex
Fixed ref bug

--- 2013-11-16 LaTeX/paper.tex
@@
 \usepackage{url}
-\usepackage{caption}
 % \usepackage{fullpage}
@@
 First and foremost, if you look at Zone 2, you see two paths going out to Zones 1 and 3, respectively.
-Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 5 is slightly larger, and you are more likely to save more people.
+Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 2 is slightly larger, and you are more likely to save more people.
 Furthermore, the overall population density of the three zones (1+2+3) is large, weighing Zone 2 as one of the more important nodes on the graph.
@@
 
-Finally, if you look at Zone 3, you see that while though redundant, the overall population covered by having an ambulance stationed there is the next greatest.
-For that reason, it makes the most sense to place the third ambulance in Zone 3.
+Finally, if you look at Zone 1, you see that while though redundant, the additional population covered by having an ambulance stationed there is the next greatest.
+For that reason, it makes the most sense to place the third ambulance in Zone 1.
 
@@
 This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.
+
+For each of these scenarios, our greedy heuristic got the exact same answer as the
+brute-force algorithm as well as the intuitive solution from the graph.
+Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing efficiently and accurately.
 

### 2013-11-16 LaTeX/paper.tex

--- 2013-11-16 LaTeX/paper.tex
@@
 brute-force algorithm as well as the intuitive solution from the graph.
-Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing extremely efficiently and accurately.
+Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing efficiently and accurately.
 

### 2013-11-16 LaTeX/paper.tex
Add 2.2

@@
 \usepackage{setspace}
-% \usepackage{minted}
-% \usemintedstyle{colorful}
+\usepackage{minted}
+\usemintedstyle{colorful}
 \graphicspath{{./Pictures/}}
@@
         Travel...
+        Travel times...
     \item[2. Zone to Zone Travel] \hfill \\
@@
 \subsection{Zone-to-Zone Population Dynamics}
-An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
-that the ambulance can cover in a second zone from a first zone (not necessarily distinct),
-will be hereafter referred to as zone-to-zone coverage.
+The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage.
+Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.
 
@@
 This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.
+See Figure \ref{B(t)}.
 
@@
   \caption{An example of a zone's population density as a function of travel time from another zone.}
-  \label{fig:sub1}
+  \label{B(t)}
 \end{subfigure}%
@@
   \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
-  \caption{TODO(drew)}
-  \label{fig:sub2}
+  \caption{The width of A and B are shown. $T_{AB} $ is the travel time between the centers (i.e. the provided average).}
+  \label{A(t)B(t)}
 \end{subfigure}
-\label{fig:test}
+\caption{Examples of population density as a function of travel time}
+\label{examples}
 \end{figure}
 
-The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
 \newpage
@@
 \begin{center}
-\includegraphics[width=3.5in]{A(t)B(t).png}
-\caption{TODO(drew)}
-\label{A(t)B(t)}
+\includegraphics[width=3.5in]{6point.pdf}
+\caption{A graph of the nodes (zones) and edges (travel times).}
+\label{satan1}
 \end{center}
@@
 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3.5in]{greedy6point.pdf}
+\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
+\label{satan2}
+\end{center}
+\end{figure}
+
+%TODO: We are trying to find zone-to-zone coverage...
+
 \begin{description}
+    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
+    	The zone-to-zone coverage function of B from A
     \item[$\mathbf{A(t), B(t)}$] \hfill \\
-    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
-    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
-    	Zone-to-zone coverage of B from A
+    	Probability density functions with respect to travel time from the center of A
     \item[$\mathbf{v}$] \hfill \\
@@
 %TODO: Graphical representation of origin and setup
+% Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
 
-The function for zone-to-zone coverage in respect to travel time can be written out as
+The function for zone-to-zone coverage in respect to travel time can be written as the product of the population of B with the percent of the population that is covered from A in less than $v$ minutes.
+The percent is the area under the probability curve, $B(t)$.
+As shown in Figure \ref{A(t)B(t)}, the bounds begin at $T_{AB} - \frac{b}{2}$ and end at $v$.
+If $v$ is less than $T_{AB} - \frac{b}{2}$, the coverage of B is 0.
+
 $$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
 
-In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B,
-$F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$.
-$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
+$B(t)$ is a population density function with a zone-specific constant $b$, which is the width of zone B.
+Every zone has a different $b$ and, as a result, a different $B(t)$.
+In order to find this specific $B(t)$, we must obtain $b$.
+Until then, we cannot directly evaluate $B(t)$.
 
-The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation
-of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
-$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
+Using the average travel time within B that is provided to us, we can calculate the value for $b$.
+However, since we are provided with a general average travel time within each zone---which does not account for the direction of travel---we must extrapolate both the average travel time within B towards A and within B away from A.
 
-The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A
-inside of A, $T_{A+}$, have a total average travel time of $T_A$. We can also write the ratio of $T_{A+}$ and $T_{A-}$,
-which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$. The same can be done with $T_{B}$.
-$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
-$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$
+The average travel time in the direction of A to B inside of B, $T_{B+}$, and the average travel time in the direction of B to A
+inside of B, $T_{B-}$, have a total average travel time of $T_B$. We can also write the ratio of $T_{B+}$ and $T_{B-}$,
+which is equivalent to the ratio of $T_{AB}$ and $T_{BA}$.
+$$T_B = \frac{T_{B+} + T_{B-}}{2}$$
 $$\frac{T_{B+}}{T_{B-}} = \frac{T_{AB}}{T_{BA}}$$
 
-This allows us to solve for $T_{A-}$  and $T_{B+}$.
-$$T_{A-} = \frac {2T_A}{1+ \frac{T_{BA}}{T_{AB}}}$$
+This allows us to solve for $T_{B+}$.
 $$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}}$$
+
+Now that we have the average travel time within B away from A, we can set that equal to the definition of the average travel time within B away from A, as shown below, and solve for the $b$ originally sought.
+The definition is  the area under the distribution of all the possible travel times from one random point in B to another point in B.
+
+$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}} = \int^b_0 s F_B(s) ds$$
+
+To find this distribution of travel times, we take the cross correlation of $B(t)$ on itself, with $s$ being  travel time plotted against frequency.
+$$F_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) B(t-s) dt$$
+
+Combining the previous two equations, we can finally solve for $b$ in terms of known values.
+$b$ is a zone-specific constant embedded within the general equation $B(t)$.
+Depending on the type of equation that $B(t)$ is, $b$ can be solved for in different ways.
+
+$$\frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}} = \int^b_0 \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s B(t) B(t-s) dt ds$$
+
+With $b$ solved and $B(t)$ fully defined, we can finally evaluate the original integral for zone-to-zone coverage.
+
+$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
 
@@
 \includegraphics[width=3in]{greedy6point.pdf}
-\caption{Graph in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
+\caption{Graph in fig. 2, with edges longer than 8 minutes removed}
 \end{center}
@@
 
-% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
+\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
 

### 2013-11-16 LaTeX/paper.tex
Adding memo stub
merge
incorrect math fixed

--- 2013-11-16 LaTeX/paper.tex
@@
 \label{fig:fullgraph}
+\caption{Graph of zones, populations, and travel times}
 \begin{center}
 \includegraphics[width=3in]{6point.pdf}
-\caption{Graph of zones, populations, and travel times}
 \end{center}
@@
 
-Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 3 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes.
+Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 1 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes.
 Therefore, it shouldn't be surprising that when we ran the greedy algorithm for $n=3$ we got that ambulances should be placed in zones
-2, 5, and 3.
-When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of zone 1, accounting for a majority of the county.
+2, 5, and 1.
+When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 1-2, 4-6 and most (28333/30000) of zone 3, accounting for a majority of the county.
 
@@
 When we ran the greedy algorithm for $n=2$ we got that ambulances should be placed in zones
-2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half      (25000/50000) of zone 1, and none of zone 3.
+2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of zone 1, and most (28333/30000) of zone 3.
 
@@
 Finally, when we ran the greedy algorithm for $n=1$ we found that our ambulance should be placed in zone 2.
-This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.
+This arrangement allows the single ambulance to cover zone 2 and parts of 1 and 3, which represents the highest population on the map.
 

### 2013-11-16 LaTeX/paper.tex

--- 2013-11-16 LaTeX/paper.tex
@@
 \includegraphics[width=3in]{greedy6point.pdf}
-\caption{Graph in fig. 2, with edges longer than 8 minutes removed}
+\caption{Graph in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
 \end{center}

### 2013-11-16 LaTeX/paper.tex
Fixed figures
Added memo

@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{6point.pdf}
-\caption{A graph of the nodes (zones) and edges (travel times).}
-\label{satan1}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{greedy6point.pdf}
-\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
-\label{satan2}
-\end{center}
-\end{figure}
-
 %TODO: We are trying to find zone-to-zone coverage...
@@
 \begin{figure}[htbp]
-\label{fig:fullgraph}
-\caption{Graph of zones, populations, and travel times}
 \begin{center}
 \includegraphics[width=3in]{6point.pdf}
+\caption{Graph of zones, populations, and travel times}
+\label{fig:fullgraph}
 \end{center}
@@
 \section{Non-Technical Memo}
-A county with a six zones needs to maximize the number of people that can be reached within eight minutes using its three ambulances.
-Given the average amount of time necessary to travel  between each of the zones, we must develop an algorithm for determining the optimal placement of the ambulances.
+To whom it may concern,
+After looking at several scenarios, and forming a strategic model, we believe that we have some
+suggestions for you regarding how to optimize ambulance placement across zones in your county.
 
-In order to solve this problem, we first needed to develop a firm understanding of how many people a single ambulance can reach within eight minutes.
-In order to get an accurate representation of how many people an ambulance can actually reach, we took into account the fact that a zone is has an area and that the population of a zone is spread out over its entire area.
-While we assumed that the population density is linear, we designed our solution to be flexible enough to implement  any  symmetrical population distribution.
+To us, it seems that the problem is as follows:  A county with a six zones needs to maximize the
+number of people that can be reached within eight minutes using its three ambulances. Given the
+average amount of time necessary to travel between each of the zones, we must determine the optimal
+placement of the ambulances to meet the three conditions.
 
-Because distance in this scenario is unknown, we are forced to use another unit to represent the population density.
-Given that we want to travel from zone A to zone B, we chose to model the population density of zone B as a function of travel time from zone A.
-Using this function, we were able to calculate the time it would take to travel through all of B (the width) and the number of people covered in B per travel time away from A.
-By taking the number of people covered and the given travel times between each of the zones, we were able to calculate the theoretical number of people reachable within eight minutes by an ambulance for each zone.
+In order to solve this problem, we first needed to develop a firm understanding of how many people
+a single ambulance can reach within eight minutes. To get an accurate representation of how many
+people an ambulance can actually reach, we took into account the fact that a zone has an area and
+that instead of being concentrated at one specific point, the population of a zone is spread out
+over its entire area. For our purposes, we assumed that the population density distribution was linear,
+but without some additional data, it is impossible for us to draw any significant conclusions about
+what it should be. However, we designed our solution to be flexible enough to implement any
+symmetrical population distribution, thereby ensuring that our model will work regardless of the data provided.
 
-After calculating the maximum number of people coverable by one ambulance, we still need to figure out where we should put the ambulances to cover the most people.
-We approach this problem in two ways: we use a brute-force method, enumerating all possible combinations of ambulance positions, and picking the one that covered the most people; we also create a greedy heuristic, which doesn’t necessarily pick the optimal solution but runs much more quickly than the brute-force algorithm, and has proven to be very robust as well.
+Because distance in this scenario is an unknown quantity (We are only given travel times in the data
+provided to us), we are forced to use another unit to represent the population density. Given that we
+want to travel from zone A to zone B, we chose to model the population density of zone B as a function
+of travel time from zone A. Using this function, we were able to calculate how many people we would be
+able to reach in B (within a timespan of eight minutes) from A. By taking the number of people covered
+and the given travel times between each of the zones, we were able to calculate how many people an
+ambulance could reach in an eight minute period from any zone A.
+
+After computing this quantity, we still need to figure out where we should put the ambulances to cover
+the most people. We approach this problem in two ways: first, we use a brute-force method, enumerating
+all possible combinations of ambulance positions, and picking the one that covered the most people
+(finding us the optimal solution); second, using our brute-force algorithm as a base, we create a greedy
+heuristic, which finds a solution relatively quickly in comparison, especially for larger cities/more
+ambulances. However, while the brute-force algorithm is guaranteed to pick the optimal solution, the greedy
+heuristic is only guaranteed to find a good one. Yet, especially when this problem is scaled up to multiple
+zones or counties, the greedy heuristic proves to be superior than the brute-force algorithm, with a high
+level of efficacy and precision.
+
+When applied to the county at hand, the greedy heuristic succeeded in finding a solution. Better yet, when
+compared to the brute-force algorithm, we found that the two methods yielded identical solutions, meaning that
+the greedy algorithm found the optimal solution as well. The results are as follows: For 3 ambulances across
+the county, we split them between zones 1, 2, and 5; this allows us to cover all of zones 1-2, 4-6 and 94\%
+of zone 3, covering 99.4\% of the county population-wise in eight minutes. If one or two ambulances are busy,
+the other two ambulances should be relocated to zones 5 and 2; ambulances in zones 5 and 2 will cover 90.1\%
+of the county, and a single ambulance in zone 2 will cover 49.4\% of the county. These results indicate that
+a majority of the county will be covered at any given time, and that all citizens can be reached in under 8 minutes.
+
+With these suggestions in mind, I hope you take the necessary steps to implement our solution in this county,
+and perhaps in others as well.
 

### 2013-11-16 LaTeX/paper.tex
Edits

@@
 \subsection{Zone-to-Zone Population Dynamics}
-The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage.
-Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.
-
-A lack of spatial understanding of the county entails the use of a different type of population density.
-Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point.
-This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.
-See Figure \ref{B(t)}.
 
@@
 
-%TODO: We are trying to find zone-to-zone coverage...
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3.5in]{6point.pdf}
+\caption{A graph of the nodes (zones) and edges (travel times).}
+\label{satan1}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=3.5in]{greedy6point.pdf}
+\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
+\label{satan2}
+\end{center}
+\end{figure}
+
+The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage.
+Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.
+
+A lack of spatial understanding of the county entails the use of a different type of population density.
+Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point.
+This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.
+See Figure \ref{B(t)}.
+
+Because we have more than four different zones, it is not possible for every zone to be adjacent with all the other zones.
+Therefore, the ambulance may travel through another zone C in an optimal route between zones A and B.
+However, we are only calculating the zone-to-zone population coverage of B from A, we can consider any time spent in zone C as a gap (i.e.
+containing a population density of 0).
+The zone-to-zone coverage of C from A is already accounted for in a separate calculation of A to C.
+
+The following calculations are used to find the coverage function for any pair of zones.
+Separate calculations must be done for every pair, as we as for both directions for each pair.
+We will be using the following variables, equations, and constants:
 
@@
     \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
-    	The zone-to-zone coverage function of B from A
-    \item[$\mathbf{A(t), B(t)}$] \hfill \\
-    	Probability density functions with respect to travel time from the center of A
-    \item[$\mathbf{v}$] \hfill \\
-    	Required ambulance response time
-    \item[$\mathbf{T_{AB}}$] \hfill \\
-    	Travel time from A to B, given
-    \item[$\mathbf{T_{BA}}$] \hfill \\
-    	Travel time from B to A, given
-    \item[$\mathbf{P_B}$] \hfill \\
-    	Total population of B
-    \item[$\mathbf{F_B(s)}$] \hfill \\
-    	The probability curve for differences in travel time within B
-   \item[$\mathbf{T_A}$] \hfill \\
-    	Average travel time inside of A
-    \item[$\mathbf{T_{A+}}$] \hfill \\
-    	Average travel time in the direction of B to A inside of A
-    \item[$\mathbf{T_{A-}}$] \hfill \\
-    	Average travel time in the direction of A to B inside of A
-   \item[$\mathbf{T_B}$] \hfill \\
-    	Average travel time inside of B
-    \item[$\mathbf{T_{B+}}$] \hfill \\
-    	Average travel time in the direction of A to B inside of B
-    \item[$\mathbf{T_{B-}}$] \hfill \\
-    	Average travel time in the direction of B to A inside of B
+    	The zone-to-zone coverage function of B from A; to be solved
+    \item[$\mathbf{B(t)}$] \hfill \\
+    	Probability density function of zone B with respect to travel time (from the center of A)
    \item[$\mathbf{a, b}$] \hfill \\
     	Width of A and B respectively
-    \item[$\mathbf{g}$] \hfill \\
-    	Width of the gap between A and B
+    \item[$\mathbf{v}$] \hfill \\
+    	Required ambulance response time; given (8 minutes)
+    \item[$\mathbf{T_{AB}, T_{BA}}$] \hfill \\
+    	Travel time from A to B and travel time from B to A; given
+    \item[$\mathbf{P_B}$] \hfill \\
+    	Total population of B; given
+   \item[$\mathbf{T_B}$] \hfill \\
+    	Average travel time inside of B; given
+    \item[$\mathbf{T_{B+}, T_{B-}}$] \hfill \\
+    	Average travel time inside of B in the direction of A to B\\Average travel time inside of B in the direction of B to A
+    \item[$\mathbf{F_B(s)}$] \hfill \\
+	  Frequency distribution of travel times from one random point in zone B to another point in B
 \end{description}
-
-%TODO: Graphical representation of origin and setup
-% Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
 

### 2013-11-16 LaTeX/paper.tex
Fix assumptions

@@
 \begin{description}
-    \item[TODO(drew): Add these assumptions] \hfill \\
-    	* Each zone is not a point, but rather a distribution. We experimented with...
-        * Route frequency is correlated with population frequency (two random variables?)
-    \item[1. Naming] \hfill \\
-    	A county is another name for a county. ... TODO(drew)
-        Travel...
-        Travel times...
-    \item[2. Zone to Zone Travel] \hfill \\
+    \item[1. Zones as Regions] \hfill \\
+    	Each zone is not a point, but rather a region with a finite area. This means that the population of each zone is not concentrated on one point, but rather is spread out across its area.
+    \item[2. Evenly Distributed Populations within Zones]\hfill \\
+    	We assume, for lack of better data, that population is evenly distributed in each zone.
+    \item[3. Zone to Zone Travel] \hfill \\
     	The travel times given are considered to be optimal routes from the center of one zone to
-        the center of the another, regardless of any other zones that may lie in between.
-    \item[3. Travel Inside Each Zone] \hfill \\
+        the center of the another, regardless of any other zones that may lie in between. The time to travel from one zone to another is not necessarily equal to the reverse.
+    \item[4. Travel Inside Each Zone] \hfill \\
     	The travel times given for travel from any zone to itself is the average
         of all the travel times of the different routes within that zone.
-    \item[4. Directional Travel Inside Each Zone] \hfill \\
-    	The ratio between the time it takes inside a zone to travel toward a second zone,
-        to the time it takes inside a zone to return from a second, is equal to the ratio
-        between the travel time from the first zone to the second, and the travel time from the
-        second to the first.
-    \item[5. Ambulance Placement] \hfill \\
+    \item[5. Directional Travel Inside Each Zone] \hfill \\
+    	The ratio of the time it takes to travel inside zone A toward a second zone B
+        to the time it takes to travel inside zone A away from zone B, is equal to the ratio
+        of travel time from A to B compared to the travel time from B to A. For example, traffic congestion from A to B  slows down all movement in that direction, even inside A.
+    \item[6. Ambulance Placement] \hfill \\
         Ambulances can only be placed in the very center of a zone. Because we do not know the
@@
         being closer to one zone or another.
-    \item[6. Partial Coverage] \hfill \\
+    \item[7. Partial Coverage] \hfill \\
         Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
@@
 
+Although our model is robust and supports any symmetrical function for $B(t)$, we assume for lack of better data that population is evenly distributed in each zone (i.e.
+$B(t)$ is a constant).
+This simplifies the process of finding the optimal ambulance locations.
+
 \subsection{Ambulance Distribution Optimization}
@@
 the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
-of the individual zones, i.e. the number of people that can be reached by at least one ambulance
-within eight minutes.
+of the individual zones (i.e. the number of people that can be reached by at least one ambulance
+within eight minutes).
 

### 2013-11-22 LaTeX/paper.tex
final

@@
 \label{examples}
-\end{figure}
-
-\newpage
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{6point.pdf}
-\caption{A graph of the nodes (zones) and edges (travel times).}
-\label{satan1}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=3.5in]{greedy6point.pdf}
-\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
-\label{satan2}
-\end{center}
 \end{figure}
@@
         \textbf{Strengths} & \textbf{Weaknesses}\\
-        \hline
-        1.
+        \hline 1.
 Our model, by virtue of its polynomial-time greedy selection algorithm, is extremely scalable.
@@
 To whom it may concern,
+
 After looking at several scenarios, and forming a strategic model, we believe that we have some
@@
 \section{Code}
-The following contains the code for both our brute force location optimizer, as well as the greedy optimizer.
+The following Python script (optimizer.py) contains the code for both our brute force location optimizer, as well as the greedy optimizer.
 Both functions take a parameter $nambulances$, representing the total number of ambulances we have to allocate across the county.
+\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
 
-% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
+The following file (data.py) contains the data we used for running our optimizer, taken from the provided problem constraints.
+\inputminted[fontsize=\footnotesize]{python}{../Code/data.py}
 
